Reliable Inferences from Simply Parameterised Models

### 2012-08-08 ms.tex
Words

\section{Example: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data in order to estimate the total flux of the line.

>>>>

\section{Example 2: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data in order to estimate the total flux of the line.

\subsection{The Simply-Parameterised Model}
The model for the shape of the line is:
\begin{eqnarray}
\mathcal{M}(x; a, b, c) &=& \exp\left[\right]
\end{eqnarray}

\subsection{The Sampling Distribution}
The sampling distribution, aka the probability distribution for the data given
the parameters, is simply a multivariate normal distribution. Note that the
gaussian error assumption should be distinguished from the assumption of a gaussian
shape for the emission line.

\begin{eqnarray}
p(\mathbf{y}|a, b, c) &=& \prod_{i=1}^N
\frac{1}{\sigma\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; a, b, c)\right)^2
\right]
\end{eqnarray}
